Multi-line Intensity Mapping

### 2019-04-15 paper/ms.tex
Add Bhigher fig to paper

@@

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics{fig/corner_Nconstant_Bhigher.pdf}
\end{center}
\caption{Caption.}
\label{fig:tf_Nconst_Bhigher}
\end{figure}

@@

In Figure~\ref{fig:tf_Nconst_Bhigher} we perform the same procedure, except
now we slightly increase the intrinsic \SN{} of $B_2$ and $B_3$ by setting
$B_2^2 = 4$ and $B_3^2 = 9$. Notice that we have not changed the intrinsic
\SN{} of field $1$. Two things are apparent. First, the strength of the
correlations that we discussed for Figure~\ref{fig:tf_Nconst} are stronger,
since the different priors have become more disparate in their relative
tightness. Second, as a consequence of the fractional \SN{} being the same for
each line, we see that the error on $B_1$ has become much smaller (and
similarly for $B_2$ and $B_3$). However, this is particularly interesting in
the case of $B_1$. No modification has been made to it's intrinsic \SN{} (or,
in other words, no additional measurements have been made of line $1$).
Nonetheless, the \SN{} on the inferred $B_1$ has become higher.
